\documentclass[a4paper,12pt]{article}



\usepackage[export]{adjustbox}
\usepackage[russian]{babel}
\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}



\usepackage{amsbsy}
\usepackage{amscd}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsopn}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsthm}
\usepackage{amsxtra}
\usepackage{array}
\usepackage{ctable}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{latexsym}
\usepackage{listings}
\usepackage{makecell}
\usepackage{ragged2e}
\usepackage{titlesec}
\usepackage{tocloft}
\usepackage{xcolor}



\renewcommand{\familydefault}{\sfdefault}

\renewcommand{\arraystretch}{1.5}

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\geometry{left   = 0.5cm}
\geometry{bottom = 0.5cm}
\geometry{right  = 0.5cm}
\geometry{top    = 0.5cm}

\parindent = 0pt
\parskip   = 0pt
\tolerance = 100

\flushbottom

\definecolor{G}{rgb}{0.00, 0.50, 0.00}

\hypersetup
{
    linkcolor  = G,
    urlcolor   = G,
    colorlinks = true
}

\renewenvironment{itemize}
{
    \begin{list}{\labelitemi}
    {
      \setlength{\topsep}{0pt}
      \setlength{\partopsep}{0pt}
      \setlength{\parskip}{0pt}
      \setlength{\itemsep}{0pt}
      \setlength{\parsep}{0pt}
      \setlength{\leftmargin}{14.5pt}
    }
}{\end{list}}

\definecolor{B}{rgb}{0.00, 0.00, 0.50}

\lstset
{
    backgroundcolor   = \color{white},      % Установка цвета заднего плана  
    basicstyle        = \ttfamily\color{B}, % Установка размера и цвета шрифта
    breakatwhitespace = true,               % Установка разрывов на пробелах
    breaklines        = true,               % Установка переноса длинных строк
    captionpos        = none,               % Установка позиции имени листинга
    commentstyle      = \color{B},          % Установка цвета комментариев кода
    deletekeywords    = {},                 % Установка удаленных ключевых слов  
    escapeinside      = {\%*}{*)},          % Установка добавления LaTeX в коде  
    extendedchars     = false,              % Установка дополнительных символов 
    frame             = L,                  % Установка типа рамки вокруг кода
    framexleftmargin  = -8pt,               % Установка размера левого отступа
    keepspaces        = true,               % Установка выравнивания пробелов
    keywordstyle      = \color{B},          % Установка цвета ключевых слов  
    language          = C++,                % Установка языка программирования
    otherkeywords     = {},                 % Установка добавочных ключевых слов   
    numbers           = none,               % Установка позиции нумерации строк
    numbersep         = 0pt,                % Установка отступа нумерации строк
    numberstyle       = \color{black},      % Установка цвета нумерации строк
    showspaces        = false,              % Установка пробелов символом '_'
    showstringspaces  = false,              % Установка пробелов символом '_'
    showtabs          = false,              % Установка табуляторов видимыми
    stepnumber        = 1,                  % Установка периода нумерации строк
    stringstyle       = \color{B},          % Установка цвета строковых литералов
    tabsize           = 2,                  % Установка размера табуляции в коде
}



\begin{document}



\newpage\thispagestyle{empty}\pdfpageheight = 2.50in\enlargethispage{100in}

\title{\bf Software Engineering} 

\author{Moscow Institute of Physics and Technology}

\date{}

\maketitle



\newpage\thispagestyle{empty}\pdfpageheight = 6.10in\enlargethispage{100in}

\renewcommand\contentsname{\Large Table of Contents}

\renewcommand{\cftdotsep}{0.5}

\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}

\makeatletter
\let\latexl@section\l@section
\def\l@section#1#2{\begingroup\let\numberline\@gobble\latexl@section{#1}{#2}\endgroup}
\makeatother

\titlelabel{}

\thispagestyle{empty}\tableofcontents\thispagestyle{empty}



\newpage\thispagestyle{empty}\pdfpageheight = 4.30in\enlargethispage{100in}

\section{01. Introduction and Brief Overview}

\begin{tabular}{!{\vrule width 1pt}L{4.1cm}!{\vrule width 1pt}L{14.9cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{General Introduction} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}
    
    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/01.01.pdf}{\texttt{01.01}} -- Software\:engineering. The\:C\texttt{++}\:programming\:language. Programming\:paradigms. Instruments. References.
    
\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{5.3cm}!{\vrule width 1pt}L{13.7cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Environment and Compiler} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/01.02.cpp}{\texttt{01.02}} -- Environment \href{https://code.visualstudio.com/}{Visual Studio Code}. Terminal. Compiler g\texttt{++} from \href{https://gcc.gnu.org/}{GCC}. Minimal program. Function \lstinline{main}.
    
\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{3.3cm}!{\vrule width 1pt}L{15.7cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Standard Library} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/01.03.cpp}{\texttt{01.03}} -- Standard library overview. Comments. Documenting code. Utility \href{https://doxygen.nl/}{Doxygen}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/01.04.hpp}{\texttt{01.04}} -- Standard library header files.
    
\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{4.7cm}!{\vrule width 1pt}L{14.3cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Version Control System} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/01.05.pdf}{\texttt{01.05}} -- Version control system \href{https://git-scm.com/}{Git}. Project hosting system \href{https://github.com/}{GitHub}. Git graphical client \href{https://www.smartgit.dev/}{SmartGit}.
    
\end{itemize}



\newpage\thispagestyle{empty}\pdfpageheight = 16.50in\enlargethispage{100in}

\section{02. Basics of Programming}

\begin{tabular}{!{\vrule width 1pt}L{5.0cm}!{\vrule width 1pt}L{14.0cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Fundamental Data Types} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}
    
    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.01.cpp}{\texttt{02.01}} -- Type \lstinline{bool}. Objects. Variables. Literals \lstinline{false} and \lstinline{true}. Operator \lstinline{sizeof}. Attribute \lstinline{maybe_unused}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.02.cpp}{\texttt{02.02}} -- Type \lstinline{char}. Escape sequences. Portability problem.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.03.cpp}{\texttt{02.03}} -- Type \lstinline{int}. Modifiers \lstinline{short} and \lstinline{long}. Literal suffixes. Overflow problem.

    \smallskip
    
    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.04.cpp}{\texttt{02.04}} -- Types \lstinline{float}, \lstinline{double} and \lstinline{long double}. Precision problem.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.05.cpp}{\texttt{02.05}} -- Type signness. Modifiers \lstinline{signed} and \lstinline{unsigned}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.06.cpp}{\texttt{02.06}} -- Constants. Qualifier \lstinline{const}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.07.cpp}{\texttt{02.07}} -- Type aliases. Declaration \lstinline{using}. Specifier \lstinline{typedef}. Fixed\,-\,width integer types.
    
\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{4.3cm}!{\vrule width 1pt}L{14.7cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Objects and Variables} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.08.cpp}{\texttt{02.08}} -- Declarations. Definitions. Default, value, direct, copy and list initialization. Undefined behavior.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.09.cpp}{\texttt{02.09}} -- Type inference. Placeholder \lstinline{auto}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.10.cpp}{\texttt{02.10}} -- Implicit, explicit, narrowing and C\,-\,style type conversions. Operator \lstinline{static_cast}.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{5.2cm}!{\vrule width 1pt}L{13.8cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Operators and Expressions} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.11.cpp}{\texttt{02.11}} -- Logical operators. Alternative representations. Short\,-\,circuit evaluations.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.12.cpp}{\texttt{02.12}} -- Expressions. Arithmetic and comparison operators. Operator arity. Operator precedence.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.13.cpp}{\texttt{02.13}} -- Operator exclusive or.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.14.cpp}{\texttt{02.14}} -- Assignment operators. Arithmetic swap algorithm. Function \lstinline{std::swap}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.15.cpp}{\texttt{02.15}} -- Operator division. Operator remainder.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.16.cpp}{\texttt{02.16}} -- Evaluation order. Unspecified behavior. Operator associativity. Operator comma.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{4.2cm}!{\vrule width 1pt}L{14.8cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Selection Statements} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.17.cpp}{\texttt{02.17}} -- Statement \lstinline{if}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.18.cpp}{\texttt{02.18}} -- Statement \lstinline{switch}. Labels \lstinline{case} and \lstinline{default}. Attributes \lstinline{fallthrough}, \lstinline{likely} and \lstinline{unlikely}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.19.cpp}{\texttt{02.19}} -- Ternary operator.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{5.7cm}!{\vrule width 1pt}L{13.3cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Loops and Jump Statements} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.20.cpp}{\texttt{02.20}} -- Statement \lstinline{for}. Two's complement.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.21.cpp}{\texttt{02.21}} -- Statement \lstinline{continue}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.22.cpp}{\texttt{02.22}} -- Statement \lstinline{break}. Infinite loops.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.23.cpp}{\texttt{02.23}} -- Statement \lstinline{goto}. Labels.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.24.cpp}{\texttt{02.24}} -- Statement \lstinline{while}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.25.cpp}{\texttt{02.25}} -- Statement \lstinline{while}\,-\,\lstinline{do}.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{4.4cm}!{\vrule width 1pt}L{14.6cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Memory Management} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.26.cpp}{\texttt{02.26}} -- Pointers. Operator address of. Operator dereference. Literal \lstinline{nullptr}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.27.cpp}{\texttt{02.27}} -- Constant pointers. Pointers to constants.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{5.3cm}!{\vrule width 1pt}L{13.7cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Collections and Containers} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.28.cpp}{\texttt{02.28}} -- Static arrays. Aggregate initialization.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.29.cpp}{\texttt{02.29}} -- Function \lstinline{std::size}. Index access operator. Pointer arithmetic.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.30.cpp}{\texttt{02.30}} -- Dynamic objects. Operators \lstinline{new} and \lstinline{delete}. Dynamic arrays. Operators \lstinline{new[]} and \lstinline{delete[]}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.31.cpp}{\texttt{02.31}} -- Container \lstinline{std::vector} overview.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{3.6cm}!{\vrule width 1pt}L{15.4cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Lvalue References} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.32.cpp}{\texttt{02.32}} -- Lvalue references.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.33.cpp}{\texttt{02.33}} -- Constant lvalue references.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.34.cpp}{\texttt{02.34}} -- Lvalue reference type inference. Placeholder \lstinline{decltype(auto)}. Specifier \lstinline{decltype}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.35.cpp}{\texttt{02.35}} -- Utility \lstinline{std::reference_wrapper}.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{4.9cm}!{\vrule width 1pt}L{14.1cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Functional Programming} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.36.cpp}{\texttt{02.36}} -- Functions. Calling conventions. Statement \lstinline{return}. Attribute \lstinline{nodiscard}. Object \lstinline{std::ignore}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.37.cpp}{\texttt{02.37}} -- Type \lstinline{void}. Default arguments.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.38.cpp}{\texttt{02.38}} -- Passing arguments. Container \lstinline{std::span}. Function overloading.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.39.cpp}{\texttt{02.39}} -- Storage durations. Dangling pointers and references. Automatic and static objects. Specifier \lstinline{static}.

    \smallskip
    
    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.40.cpp}{\texttt{02.40}} -- Inline functions. Specifier \lstinline{inline}. Special memory. Qualifier \lstinline{volatile}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.41.cpp}{\texttt{02.41}} -- Recursion. Factorial. Binomial coefficients. Catalan numbers.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.42.cpp}{\texttt{02.42}} -- Insertion, merge and hybrid sort algorithms. Timsort algorithm. Function \lstinline{std::midpoint}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/02.43.cpp}{\texttt{02.43}} -- Binary search algorithm.

\end{itemize}



\newpage\thispagestyle{empty}\pdfpageheight = 13.90in\enlargethispage{100in}

\section{03. Object\,-\,Oriented Programming}

\begin{tabular}{!{\vrule width 1pt}L{5.1cm}!{\vrule width 1pt}L{13.9cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{User\,-\,defined Data Types} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.01.cpp}{\texttt{03.01}} -- Structures. Declaration \lstinline{struct}. Data members. Instances. Designated initialization.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.02.cpp}{\texttt{03.02}} -- Operator point. Operator arrow.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.03.cpp}{\texttt{03.03}} -- Classes. Declaration \lstinline{class}. Encapsulation. Specifiers \lstinline{public} and \lstinline{private}. Constructors. Destructors.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.04.cpp}{\texttt{03.04}} -- Member functions. Constant member functions.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.05.cpp}{\texttt{03.05}} -- Nested classes. Pointer \lstinline{this}. Logical and bitwise constancy. Specifier \lstinline{mutable}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.06.cpp}{\texttt{03.06}} -- Static members.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{3.8cm}!{\vrule width 1pt}L{15.2cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Interclass Relations} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.07.cpp}{\texttt{03.07}} -- Composition, aggregation, association and dependency relations.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.08.cpp}{\texttt{03.08}} -- Friend functions and classes. Specifier \lstinline{friend}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.09.cpp}{\texttt{03.09}} -- Pattern PassKey.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.10.cpp}{\texttt{03.10}} -- Pattern Attorney\,-\,Client.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{5.4cm}!{\vrule width 1pt}L{13.6cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Inheritance and Hierarchies} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.11.cpp}{\texttt{03.11}} -- Class hierarchies. Base and derived classes. Public inheritance. Protected members. Specifier \lstinline{protected}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.12.cpp}{\texttt{03.12}} -- Private inheritance. Composition.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.13.cpp}{\texttt{03.13}} -- Multiple inheritance. Virtual inheritance. Diamond problem.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.14.pdf}{\texttt{03.14}} -- Appendix: scheme.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.15.cpp}{\texttt{03.15}} -- Empty classes. Empty base optimization. Attribute \lstinline{no_unique_address}.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{4.7cm}!{\vrule width 1pt}L{14.3cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Dynamic Polymorphism} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.16.cpp}{\texttt{03.16}} -- Virtual functions. Specifiers \lstinline{virtual}, \lstinline{override} and \lstinline{final}. Virtual destructors. Abstract base classes.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.17.cpp}{\texttt{03.17}} -- Virtual pointers. Virtual tables.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.18.pdf}{\texttt{03.18}} -- Appendix: scheme.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.19.cpp}{\texttt{03.19}} -- Covariant return types.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{5.5cm}!{\vrule width 1pt}L{13.5cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Runtime Type Identification} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.20.cpp}{\texttt{03.20}} -- Downcasting type conversions. Operator \lstinline{dynamic_cast}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.21.cpp}{\texttt{03.21}} -- Operator \lstinline{typeid}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.22.cpp}{\texttt{03.22}} -- Library \href{https://www.boost.org/doc/libs/1_84_0/doc/html/boost_typeindex.html}{Boost.TypeIndex}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.23.cpp}{\texttt{03.23}} -- Utility \lstinline{std::any}. Function \lstinline{std::make_any}. Pointers to raw memory.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{3.6cm}!{\vrule width 1pt}L{15.4cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Rvalue References} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.24.pdf}{\texttt{03.24}} -- Lvalue, glvalue, xvalue, rvalue and prvalue expressions.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.25.cpp}{\texttt{03.25}} -- Rvalue references.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.26.cpp}{\texttt{03.26}} -- Temporary objects. Extending lifetime.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.27.cpp}{\texttt{03.27}} -- Copy and move semantics. Function \lstinline{std::move}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.28.cpp}{\texttt{03.28}} -- Member functions reference qualifiers.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.29.cpp}{\texttt{03.29}} -- Container\:\lstinline{Vector}.\:Special\:member\:functions.\:Deep\:and\:shallow\:copy.\:Copy\:and\:swap.\:Rules\:of\:0,\:3\:and\:5.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.30.cpp}{\texttt{03.30}} -- Copy elision. Return value optimization. Named return value optimization.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{4.3cm}!{\vrule width 1pt}L{14.7cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Operator Overloading} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.31.cpp}{\texttt{03.31}} -- Rational arithmetic. Type \lstinline{Rational}. User\,-\,defined type conversions. Specifier \lstinline{explicit}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.32.cpp}{\texttt{03.32}} -- Library \href{https://www.boost.org/doc/libs/1_75_0/libs/rational/rational.html}{Boost.Rational}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.33.cpp}{\texttt{03.33}} -- Three\,-\,way comparison operator. Strong ordering. Equivalence. Equality.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.34.cpp}{\texttt{03.34}} -- Weak ordering.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.35.cpp}{\texttt{03.35}} -- Unordered objects. Partial ordering.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.36.cpp}{\texttt{03.36}} -- Input and output operators.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/03.37.cpp}{\texttt{03.37}} -- Constant and non\,-\,constant index access operators. Constancy type conversions. Operator \lstinline{const_cast}.

\end{itemize}



\newpage\thispagestyle{empty}\pdfpageheight = 14.80in\enlargethispage{100in}

\section{04. Generic Programming}

\begin{tabular}{!{\vrule width 1pt}L{3.9cm}!{\vrule width 1pt}L{15.1cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Function Templates} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.01.cpp}{\texttt{04.01}} -- Function\:templates.\:Declaration\:\lstinline{template}.\:Type\:template\:parameters.\:Specifier\:\lstinline{typename}.\:Instantiating.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.02.cpp}{\texttt{04.02}} -- Full specializations. Function template overloading.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.03.cpp}{\texttt{04.03}} -- Dimov\,-\,Abrahams example.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.04.cpp}{\texttt{04.04}} -- Non\,-\,type template parameters. Passing static arrays by lvalue reference.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.05.cpp}{\texttt{04.05}} -- Variadic templates. Template and function parameter packs. Ellipsis.  Operator \lstinline{sizeof...}

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.06.cpp}{\texttt{04.06}} -- Variadic expressions. Fold expressions. Arithmetic reduce algorithm.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.07.cpp}{\texttt{04.07}} -- Tree traverse algorithm. Pointers to members.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{3.2cm}!{\vrule width 1pt}L{15.8cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Class Templates} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.08.cpp}{\texttt{04.08}} -- Class templates. Container \lstinline{Stack}. Default types. Instantiating member functions.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.09.cpp}{\texttt{04.09}} -- Class template argument deduction. Template template parameters.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.10.cpp}{\texttt{04.10}} -- Full and partial specializations.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.11.cpp}{\texttt{04.11}} -- Instantiating friend functions and operators.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{4.5cm}!{\vrule width 1pt}L{14.5cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Forwarding References} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.12.cpp}{\texttt{04.12}} -- Forwarding references. Perfect forwarding. Function \lstinline{std::forward}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.13.cpp}{\texttt{04.13}} -- Template type inference. Reference collapsing rules.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.14.cpp}{\texttt{04.14}} -- Special member function templates. Substitution failure is not an error. Metafunction \lstinline{std::enable_if}.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{3.6cm}!{\vrule width 1pt}L{15.4cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Special Templates} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.15.cpp}{\texttt{04.15}} -- Type alias templates. Container \lstinline{Array}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.16.cpp}{\texttt{04.16}} -- Variable and constant templates.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{4.2cm}!{\vrule width 1pt}L{14.8cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Constant Expressions} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.17.cpp}{\texttt{04.17}} -- Template metaprogramming. Compile\,-\,time factorial.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.18.cpp}{\texttt{04.18}} -- Compile\,-\,time prime number test algorithm.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.19.cpp}{\texttt{04.19}} -- Constant expressions. Immediate functions. Specifiers \lstinline{constexpr}, \lstinline{consteval} and \lstinline{constinit}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.20.cpp}{\texttt{04.20}} -- Statement \lstinline{if constexpr}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.21.cpp}{\texttt{04.21}} -- Hybrid template metaprogramming. Compile\,-\,time rational arithmetic.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.22.cpp}{\texttt{04.22}} -- Utility \lstinline{Tuple}. Dependent names. Ambiguity problem.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.23.cpp}{\texttt{04.23}} -- Utility \lstinline{std::tuple}. Functions \lstinline{std::make_tuple}, \lstinline{std::get} and \lstinline{std::tie}. Structured bindings.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{3.2cm}!{\vrule width 1pt}L{15.8cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Trait Templates} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.24.cpp}{\texttt{04.24}} -- Metafunctions \lstinline{is_same}. Base classes \lstinline{std::false_type} and \lstinline{std::true_type}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.25.cpp}{\texttt{04.25}} -- Metafunctions \lstinline{is_any_of} and \lstinline{is_all_of}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.26.cpp}{\texttt{04.26}} -- Integral arithmetic types. Metafunctions \lstinline{is_integral}. Base class \lstinline{std::integral_constant}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.27.cpp}{\texttt{04.27}} -- Metafunctions \lstinline{is_array}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.28.cpp}{\texttt{04.28}} -- Metafunctions \lstinline{add_lvalue_reference} and \lstinline{add_rvalue_reference}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.29.cpp}{\texttt{04.29}} -- Metafunctions \lstinline{remove_reference}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.30.cpp}{\texttt{04.30}} -- Metafunctions \lstinline{is_base_of}. Variadic functions.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.31.cpp}{\texttt{04.31}} -- Unevaluated contexts. Function \lstinline{declval}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.32.cpp}{\texttt{04.32}} -- Metafunctions \lstinline{is_polymorphic}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.33.cpp}{\texttt{04.33}} -- Metafunctions \lstinline{is_convertible}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.34.cpp}{\texttt{04.34}} -- Compile\,-\,time conditions. Metafunctions \lstinline{enable_if}.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{5.1cm}!{\vrule width 1pt}L{13.9cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Concepts and Constraints} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.35.cpp}{\texttt{04.35}} -- Concepts. Declaration \lstinline{concept}. Constraints. Concepts \lstinline{same_as}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.36.cpp}{\texttt{04.36}} -- Simple, type and compound requirements. Expression \lstinline{requires}. Concepts \lstinline{totally_ordered}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.37.cpp}{\texttt{04.37}} -- Requires clauses. Concept \lstinline{std::integral}. 

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{3.8cm}!{\vrule width 1pt}L{15.2cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Variadic Type Lists} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/04.38.cpp}{\texttt{04.38}} -- Compile\,-\,time type collections. Container \lstinline{Deque}. 

\end{itemize}



\newpage\thispagestyle{empty}\pdfpageheight = 8.90in\enlargethispage{100in}

\section{05. Software Architecture Patterns}

\begin{tabular}{!{\vrule width 1pt}L{3.9cm}!{\vrule width 1pt}L{15.1cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Generative Patterns} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.01.cpp}{\texttt{05.01}} -- Pattern Builder. 

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.02.cpp}{\texttt{05.02}} -- Pattern Factory method.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.03.cpp}{\texttt{05.03}} -- Pattern Abstract factory. 

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.04.cpp}{\texttt{05.04}} -- Pattern Prototype. Virtual constructors.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.05.cpp}{\texttt{05.05}} -- Pattern Singleton. Default and deleted special member functions. Specifiers \lstinline{default} and \lstinline{delete}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.06.cpp}{\texttt{05.06}} -- Pattern Noncopyable. Library \href{https://www.boost.org/doc/libs/1_85_0/libs/core/doc/html/index.html}{Boost.Noncopyable}.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{3.8cm}!{\vrule width 1pt}L{15.2cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Structural Patterns} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.07.cpp}{\texttt{05.07}} -- Pattern Adapter. 

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.08.cpp}{\texttt{05.08}} -- Pattern Bridge. 

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.09.cpp}{\texttt{05.09}} -- Pattern Composite. 

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.10.cpp}{\texttt{05.10}} -- Pattern Decorator.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.11.cpp}{\texttt{05.11}} -- Pattern Facade.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{3.9cm}!{\vrule width 1pt}L{15.1cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Behavioral Patterns} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.12.cpp}{\texttt{05.12}} -- Pattern Memento.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.13.cpp}{\texttt{05.13}} -- Pattern Observer.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.14.cpp}{\texttt{05.14}} -- Pattern State. Finite\,-\,state machines. Forward declarations.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.15.cpp}{\texttt{05.15}} -- Pattern Strategy.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.16.cpp}{\texttt{05.16}} -- Pattern Template method. Non\,-\,virtual interfaces.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{3.7cm}!{\vrule width 1pt}L{15.3cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Template Patterns} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.17.cpp}{\texttt{05.17}} -- Static polymorphism. Eliminating virtuality.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.18.cpp}{\texttt{05.18}} -- Curiously recurring template pattern.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.19.cpp}{\texttt{05.19}} -- Mixin based pattern Singleton.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.20.cpp}{\texttt{05.20}} -- Pattern Controller.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.21.cpp}{\texttt{05.21}} -- Extending functionality. Barton\,-\,Nackman trick. Restricted template expansion.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.22.cpp}{\texttt{05.22}} -- Library \href{https://www.boost.org/doc/libs/1_84_0/libs/utility/doc/html/utility/utilities/operators.html}{Boost.Operators}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.23.cpp}{\texttt{05.23}} -- Mixin based pattern Memento. Inverted inheritance.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/05.24.cpp}{\texttt{05.24}} -- Variadic base classes.

\end{itemize}



\newpage\thispagestyle{empty}\pdfpageheight = 8.80in\enlargethispage{100in}

\section{06. Projects and Libraries}

\begin{tabular}{!{\vrule width 1pt}L{4.0cm}!{\vrule width 1pt}L{15.0cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Preprocessing Stage} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.01.pdf}{\texttt{06.01}} -- Multi\,-\,file projects. Build stages. Source and header files. Translation units. Object and executable files.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.02.cpp}{\texttt{06.02}} -- Preprocessor. Directives \lstinline{include}, \lstinline{define}, \lstinline{undef},  \lstinline{if}, \lstinline{else}, \lstinline{endif} and \lstinline{pragma}. Macros. 

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.03.cpp}{\texttt{06.03}} -- Macros \lstinline{FILE}, \lstinline{LINE}, \lstinline{DATE}, \lstinline{TIME} and others. Identifier \lstinline{func}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.04.cpp}{\texttt{06.04}} -- Utility \lstinline{std::source_location}.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{4.9cm}!{\vrule width 1pt}L{14.1cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Compilation and Linkage} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.05.hpp}{\texttt{06.05}} -- Conditional compilation. Include guards. One definition rule. Specifier \lstinline{extern}. Inline variables.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.06.hpp}{\texttt{06.06}} -- Precompiled header files.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.07.cpp}{\texttt{06.07}} -- Global variables and constants. Anonymous namespaces.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.08.cpp}{\texttt{06.08}} -- Internal and external linkage. Multiply defined and unresolved external symbols.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.09.hpp}{\texttt{06.09}} -- Reducing compile\,-\,time dependencies. Pointers to implementations.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.10.cpp}{\texttt{06.10}} -- Class implementation details.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.11.cpp}{\texttt{06.11}} -- Appendix: main.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.12.cpp}{\texttt{06.12}} -- Namespaces. Declaration \lstinline{namespace}. Scope operator. Argument dependent lookup. Namespace aliases.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{3.2cm}!{\vrule width 1pt}L{15.8cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Module Support} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.13.cxx}{\texttt{06.13}} -- Modules. Declaration \lstinline{module}. Global module fragments. Exporting symbols. Declaration \lstinline{export}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.14.cxx}{\texttt{06.14}} -- Interface and implementation units. Standard library modules.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.15.cxx}{\texttt{06.15}} -- Submodules.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.16.cpp}{\texttt{06.16}} -- Importing modules. Declaration \lstinline{import}.

    \smallskip

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{5.1cm}!{\vrule width 1pt}L{13.9cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Build Automation System} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/CMakeLists.txt}{\texttt{06.17}} -- Builder \href{https://cmake.org/}{CMake}. File CMakeLists. Packages. Targets. Libraries. Scripts.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{3.3cm}!{\vrule width 1pt}L{15.7cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Custom Libraries} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/06.18.cpp}{\texttt{06.18}} -- Importing symbols and aliases. Library \href{https://www.boost.org/doc/libs/1_84_0/doc/html/boost_dll.html}{Boost.DLL}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/library_v1/source/06.19.hpp}{\texttt{06.19}} -- Static libraries.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/library_v1/source/06.20.cpp}{\texttt{06.20}} -- Library implementation details.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/library_v2/source/06.21.cpp}{\texttt{06.21}} -- Dynamic libraries. C\,-\,style linkage. Declaration \lstinline{extern C}. Implicit and explicit library linkage.

\end{itemize}



\newpage\thispagestyle{empty}\pdfpageheight = 8.20in\enlargethispage{100in}

\section{07. Handling Errors and Debugging}

\begin{tabular}{!{\vrule width 1pt}L{3.7cm}!{\vrule width 1pt}L{15.3cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Code Interruptions} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.01.cpp}{\texttt{07.01}} -- Compile\,-\,time and runtime assertions. Declaration \lstinline{static_assert}. Macro \lstinline{assert}. 

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.02.cpp}{\texttt{07.02}} -- Normal and abnormal exits. Functions \lstinline{std::atexit}, \lstinline{std::exit}, \lstinline{std::abort} and \lstinline{std::terminate}.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{4.4cm}!{\vrule width 1pt}L{14.6cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Return Code Handling} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.03.cpp}{\texttt{07.03}} -- Return codes. Macro \lstinline{errno}. Function \lstinline{std::strerror}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.04.cpp}{\texttt{07.04}} -- Scoped and unscoped enumerations. Declaration \lstinline{enum}. Underlying types.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.05.cpp}{\texttt{07.05}} -- Unions. Declaration \lstinline{union}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.06.cpp}{\texttt{07.06}} -- Hybrid return codes. Utility \lstinline{Alternative}. Anonymous unions.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.07.cpp}{\texttt{07.07}} -- Utility \lstinline{std::variant}. Type \lstinline{std::monostate}. Functions \lstinline{std::get}, \lstinline{std::visit} and others.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.08.cpp}{\texttt{07.08}} -- Ternary logic. Library \href{https://www.boost.org/doc/libs/1_85_0/doc/html/tribool.html}{Boost.Tribool}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.09.cpp}{\texttt{07.09}} -- Utility \lstinline{std::optional}. Object \lstinline{std::nullopt}. Function \lstinline{std::make_optional}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.10.cpp}{\texttt{07.10}} -- Utility \lstinline{std::expected}. Type \lstinline{std::unexpected}.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{3.9cm}!{\vrule width 1pt}L{15.1cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Exception Handling} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.11.cpp}{\texttt{07.11}} -- Statements \lstinline{throw}, \lstinline{try} and \lstinline{catch}. Stack unwinding. User\,-\,defined exceptions. Attribute \lstinline{noreturn}. 

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.12.cpp}{\texttt{07.12}} -- Exception safety guarantees. Specifier and operator \lstinline{noexcept}. Zero\,-\,overhead principle.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.13.cpp}{\texttt{07.13}} -- Exception safe container \lstinline{Stack} interface.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.14.cpp}{\texttt{07.14}} -- Backtracing. Call stack. Container \lstinline{std::stacktrace}.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{4.8cm}!{\vrule width 1pt}L{14.2cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Debugging and Profiling} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.15.cpp}{\texttt{07.15}} -- Debugger \href{https://sourceware.org/gdb/}{GDB}. Commands run, break, next, step, continue, print and backtrace.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.16.cpp}{\texttt{07.16}} -- Memory leaks. Profiler \href{https://valgrind.org/}{Valgrind}. Processor load. Profiler \href{https://valgrind.org/docs/manual/cl-manual.html}{Callgrind}. Visualizer \href{https://kcachegrind.sourceforge.net/html/Home.html}{KCachegrind}. Utility \href{https://htop.dev/}{htop}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.17.cpp}{\texttt{07.17}} -- Logging. Tracing. Library \href{https://www.boost.org/doc/libs/1_84_0/libs/log/doc/html/index.html}{Boost.Log}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.18.cpp}{\texttt{07.18}} -- Library \href{https://github.com/google/glog}{Google.Log}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.19.cpp}{\texttt{07.19}} -- Testing. Unit tests. Test suites and cases. Datasets. Fixtures. Library \href{https://www.boost.org/doc/libs/1_84_0/libs/test/doc/html/index.html}{Boost.Test}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.20.cpp}{\texttt{07.20}} --  Assertions. Expectations. Library \href{https://github.com/google/googletest}{Google.Test}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/07.21.cpp}{\texttt{07.21}} --  Benchmarks. Algorithmic complexity. Library \href{https://github.com/google/benchmark}{Google.Benchmark}.

\end{itemize}



\newpage\thispagestyle{empty}\pdfpageheight = 13.40in\enlargethispage{100in}

\section{08. Instruments of Calculus}

\begin{tabular}{!{\vrule width 1pt}L{3.7cm}!{\vrule width 1pt}L{15.3cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Bitwise Processing} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.01.cpp}{\texttt{08.01}} -- Number systems. Binary, octal, decimal and hexadecimal literals.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.02.cpp}{\texttt{08.02}} -- Bitwise logical operators. Bitwise swap algorithm.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.03.cpp}{\texttt{08.03}} -- Reflected binary Gray code. Gray code encode and decode algorithms.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.04.pdf}{\texttt{08.04}} -- Encoder implementation.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.05.cpp}{\texttt{08.05}} -- Bit fields. Utility \lstinline{Timestamp}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.06.cpp}{\texttt{08.06}} -- Benchmarks for bit fields.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.07.cpp}{\texttt{08.07}} -- Fixed\,-\,size sequences of bits. Utility \lstinline{std::bitset}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.08.cpp}{\texttt{08.08}} -- Enumeration \lstinline{std::byte}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.09.cpp}{\texttt{08.09}} -- Endianess. Big and little endian byte orders. Enumeration \lstinline{std::endian}. Function \lstinline{std::to_integer}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.10.cpp}{\texttt{08.10}} -- Reinterpreting bits. Operator \lstinline{reinterpret_cast}. Type punning. Function \lstinline{std::bit_cast}.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{3.3cm}!{\vrule width 1pt}L{15.7cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Long Arithmetic} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.11.cpp}{\texttt{08.11}} -- Indian exponentiation algorithm.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.12.cpp}{\texttt{08.12}} -- Factorial for type \lstinline{int}. Utility \lstinline{std::numeric_limits}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.13.hpp}{\texttt{08.13}} -- Long arithmetic. Type \lstinline{Integer}. Long arithmetic and comparison operators. Square root algorithm.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.14.pdf}{\texttt{08.14}} -- Karatsuba fast multiplication algorithm. 

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.15.cpp}{\texttt{08.15}} -- Appendix: main. 

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.16.cpp}{\texttt{08.16}} -- Factorial for type \lstinline{Integer}. 

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.17.cpp}{\texttt{08.17}} -- Extended checked and unchecked integer types. Library \href{https://www.boost.org/doc/libs/1_84_0/libs/multiprecision/doc/html/index.html}{Boost.Multiprecision}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.18.cpp}{\texttt{08.18}} -- Factorial for type \lstinline{boost::multiprecision::cpp_int}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.19.hpp}{\texttt{08.19}} -- Embedding Python. Python C\texttt{/}C\texttt{++} API. Global interpreter locker. Library \href{https://www.boost.org/doc/libs/1_84_0/libs/python/doc/html/index.html}{Boost.Python}. 

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.20.cpp}{\texttt{08.20}} -- Factorial for type \lstinline{boost::python::api::object}. Module \lstinline{math}.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{4.1cm}!{\vrule width 1pt}L{14.9cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Floating Point Types} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.21.cpp}{\texttt{08.21}} -- Precision. Exponent. Infinity. Quiet and signaling NaNs. Standard IEEE\,-\,754.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.22.cpp}{\texttt{08.22}} -- Floating\;point\;numbers\;compare\;algorithms.\;Absolute\;and\;relative\:epsilon\:constants.\:Function\:\lstinline{std::abs}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.23.cpp}{\texttt{08.23}} -- Extended floating point types.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.24.cpp}{\texttt{08.24}} -- Numerical methods. Derivatives. Special math functions. Library \href{https://www.boost.org/doc/libs/1_84_0/libs/math/doc/html/index.html}{Boost.Math}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.25.cpp}{\texttt{08.25}} -- Complex numbers. Type \lstinline{std::complex}. Functions \lstinline{std::real}, \lstinline{std::imag} and others.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.26.cpp}{\texttt{08.26}} -- Discrete Fourier transform algorithm.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{3.6cm}!{\vrule width 1pt}L{15.4cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Random Numbers} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.27.cpp}{\texttt{08.27}} -- Non\,-\,deterministic generators. Entropy sources. Seeds. Engines. Distributions.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.28.pdf}{\texttt{08.28}} -- Appendix: scheme.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.29.cpp}{\texttt{08.29}} -- Monte\,-\,Carlo methods. Pi constant estimation.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.30.pdf}{\texttt{08.30}} -- Appendix: scheme.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.31.cpp}{\texttt{08.31}} -- W.\:L.\:Putnam\:mathematical\:competition\:problem.\:Probability\:estimation.\:Barycentric\:coordinate\:method.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.32.cpp}{\texttt{08.32}} -- Statistics. Weighted mean and variance. Library \href{https://www.boost.org/doc/libs/1_89_0/doc/html/accumulators.html}{Boost.Accumulators}.

\end{itemize}

\bigskip\medskip

\begin{tabular}{!{\vrule width 1pt}L{4.2cm}!{\vrule width 1pt}L{14.8cm}!{\vrule width 0pt}} 

\Xcline{1-1}{1pt}

\textbf{Chrono Management} & \\

\Xcline{1-2}{1pt}

\end{tabular}

\medskip\smallskip

\begin{itemize}

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.33.cpp}{\texttt{08.33}} -- Namespace \lstinline{std::chrono}. System, steady and high\,-\,resolution clocks. Time points. Unix epoch.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.34.cpp}{\texttt{08.34}} -- Durations. Duration type conversions.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.35.cpp}{\texttt{08.35}} -- Durations since epoch. C\,-\,style time. Type \lstinline{std::time_t}. Function \lstinline{std::time}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.36.cpp}{\texttt{08.36}} -- Utility \lstinline{Timer}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.37.cpp}{\texttt{08.37}} -- Library \href{https://www.boost.org/doc/libs/1_85_0/libs/timer/doc/index.html}{Boost.Timer}.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.38.cpp}{\texttt{08.38}} -- Calendars. Years. Months. Days. Hours. Minutes. Seconds.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.39.cpp}{\texttt{08.39}} -- Time zones.

    \smallskip

    \item \href{https://github.com/i-s-m-mipt/Education/blob/master/projects/examples/source/08.40.cpp}{\texttt{08.40}} -- Namespace \lstinline{std::literals}. User\,-\,defined literals. Literal operators.

\end{itemize}

\bigskip\medskip






\newpage\thispagestyle{empty}\pdfpageheight = 1.00in\enlargethispage{100in}

\section{09. Detailed Memory Management}



\newpage\thispagestyle{empty}\pdfpageheight = 1.00in\enlargethispage{100in}

\section{10. Collections and Containers}



\newpage\thispagestyle{empty}\pdfpageheight = 1.00in\enlargethispage{100in}

\section{11. Iterators and Algorithm Libraries}



\newpage\thispagestyle{empty}\pdfpageheight = 1.00in\enlargethispage{100in}

\section{12. Text Data Processing}



\newpage\thispagestyle{empty}\pdfpageheight = 1.00in\enlargethispage{100in}

\section{13. Streams and Data Serialization}



\newpage\thispagestyle{empty}\pdfpageheight = 1.00in\enlargethispage{100in}

\section{14. Concurrent Programming}



\newpage\thispagestyle{empty}\pdfpageheight = 1.00in\enlargethispage{100in}

\section{15. Network Technologies and Tools}

\end{document}